Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-10 hscc2017/poster.tex
fixes

The design of our synthesizer is given in Figure~\ref{fig:CEGIS} and consists
of two phases, {\sc Synthesize} and {\sc Verify}, which interact via a
finite set of test vectors {\sc inputs} that is updated incrementally. 
Given the aforementioned specification $\sigma$, the {\sc synth} procedure
tries to find an existential witness $\vec{P}$ satisfying the specification
$\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc inputs} (as opposed to
all $\vec{x} \in \mathcal{D}$).
%
If {\sc synthesize} succeeds in finding a witness~$\vec{P}$, this witness
is a candidate solution to the full synthesis formula.  We pass this
candidate solution to {\sc verify}, which checks whether it is a full
solution (i.e., $\vec{P}$ satisfies the specification $\sigma(\vec{x},
\vec{P})$ for all $\vec{x}\in\mathcal{D}$).
%
If this is the case, then the algorithm terminates.  Otherwise, additional
information is provided to the {\sc synthesize} phase in the form of a new
counterexample that is added to the {\sc inputs} set and the loop iterates
again (note that, for now, we ignore the second feedback signal ``Increase
Precision'' provided by the {\sc Verify} phase in Figure~\ref{fig:CEGIS} as it
is specific to control synthesis and will be described in the next section).

It is worth noting that each iteration of the loop adds a new input to
the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
that the full set of inputs $\mathcal{D}$ is finite, this means that
the refinement loop can only iterate a potentially very large, but
finite number of times.

@@

\bibliographystyle{abbrv}
%\bibliography{paper}

>>>>

The design of our synthesizer is given in Figure~\ref{fig:CEGIS} and consists
of two phases, {\sc Synthesize} and {\sc Verify}, which interact via a
finite set of test vectors {\sc inputs} that is updated incrementally. 
Given the aforementioned specification $\sigma$, the {\sc synth} procedure
tries to find an existential witness $\vec{P}$ satisfying the specification
$\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc inputs} (as opposed to
all $\vec{x} \in \mathcal{D}$).
%
If {\sc synthesize} succeeds in finding a witness~$\vec{P}$, this witness
is a candidate solution to the full synthesis formula.  We pass this
candidate solution to {\sc verify}, which checks whether it is a full
solution (i.e., $\vec{P}$ satisfies the specification $\sigma(\vec{x},
\vec{P})$ for all $\vec{x}\in\mathcal{D}$).
%
If this is the case, then the algorithm terminates.  Otherwise, additional
information is provided to the {\sc synthesize} phase in the form of a new
counterexample that is added to the {\sc inputs} set and the loop iterates
again.

@@

\bibliographystyle{abbrv}
\bibliography{paper}
